Results

### 2020-11-27 Analysis.Rmd
atualizacao

@@

```{r warning=FALSE}
Model <- lmer(log(weight) ~ crop*planting*location + (1|year:plant), data=data)
summary(Model)
anova(Model)
```

```{r}
Model1 <- lmer(log(weight) ~ crop*planting + (1|year:plant), data=data)
```

@@

```{r}
lsm <- emmeans(Model, ~ crop * planting | location ,  adjust="none", type="response")
lsm
```

>>>>

```{r}
data %>% 
  summarise(max(doyh) - min(doyh))
```

```{r}
data %>% 
  group_by(crop, location, planting) %>% 
  summarise(mean = mean(weight), min = min(weight), max = max(weight)) %>% 
  ggplot(aes(x=planting, y=mean, fill = planting)) +
    geom_col() +
  facet_grid(location ~ crop) +
  coord_flip()
```

```{r}
data %>% 
  ggplot(aes(x = location, y = weight)) +
  geom_bar(stat="identity", fun.y = "mean") +
  facet_grid(planting ~ crop) +
  coord_flip()
```

@@

```{r warning=FALSE}
new_dt <- data %>% 
  filter(crop %in% "fallow",
         planting %in% "June") 
Model <- lmer(log(weight) ~ location + (1|year:location) + (1|plant:location), data= new_dt)
#summary(Model)
anova(Model)
```

```{r}

Model1 <- lmer(log(weight) ~ crop*planting + (1|year:plant), data=data)
```

@@

```{r}
?emmeans
```

```{r}
lsm <- emmeans(Model, ~  location ,  adjust="none", type="response")
lsm
```
